\section{Gossip Model}\label{sec:gossip_model}

\paragraph{Epoch consensus\\}

In the following the probability for the Hashgraph-algorithm to reach an Epoch consensus within $H$ events consecutive is estimated in a simple model as follows.\\

To estimate the bandwidth and the propagation delay simple simulation model has been implemented. 
The network participants are given by the flowing parameters.
\begin{itemize}
	\item[$H$] is the number of event for a node to reach Epoch-consensus.
	\item[$M$] is the total number of nodes which are available for the network (This includes active and passive nodes, not prospect nodes). 
	\item[$n$] is the number of nodes which has not yet been seen by the current node. 
\end{itemize}


\begin{table}[H]
	\begin{center}
		\begin{tabular}{|l|p{4cm}|p{3cm}|}
			\hline
			Nodes $N$ & Round Factor $n_{round}$ & Bandwidth-Scale $B$ \\
			\hline
			11 & 5 & 171 \\
			\hline
			31 & 8 & 1396 \\
			\hline
			101 & 12 & 14918 \\
			\hline
			1001 & 16 & 1498538 \\
			\hline
			10001 & 20 & 149868334 \\
			\hline
			100001 & 24 & 14996214212 \\
			\hline
		\end{tabular}
	\end{center}
	\caption{Gossip simulation model} 
	\label{tab:gossip_model}
\end{table}

From the simulation the following expression can be driven.\\

The average events per round: 
\begin{equation}
n_{round} = 2.2 \cdot ln(N) 
\end{equation}
The average estimated time between epochs: 

\begin{equation}
t_{epoch} = K \cdot n_{round} \cdot t_{net}
\end{equation}
Whe the following is defined as:
\begin{itemize}
	\item[$N$] is the number of active nodes running the networks. 
	\item[$K$] is the epoch scaling factor (Typical value of $K$ is typical a little larger than 3)
	\item[$n_{round}$] is the average events for between round. 
	\item[$t_{net}$] is the network delay. 
	\item[$t_{epoch}$] is the average propagation delay per transaction. 
\end{itemize}
\\

Estimated bandwidth scale-factor:
\begin{equation}
B = E_{size} \cdot N^2}
\end{equation}

Estimated bandwidth requirement:
\begin{equation}
BW = \frac{B}{n_{round\cdot t_{net}}}
\end{equation}

\begin{itemize}
	\item[$B$] is the average bandwidth scale factor used by a node.
	\item[$E_{size}$] is the average memory size of an event including transaction data. 
	\item[$BW$] is the average bandwidth used by a node.
\end{itemize}
