\section{Governance}
Tagion is a common resource(s) that constitutes the network, Tagion trademark, code and governance mechanisms, which are governed by a common resource governance model. The model is based on the ideas and design principles of Elinor Ostrom's work with the (self-) governing of the commons. The overall perception of resource governance in today's society is between the extremes of private or state ownership. There is a third option called Commons, which can be translated to self-governance or community governance. It is much more efficient as well when it comes to the governing of common resources, as Elinor Ostrom argues and proves. She won the Nobel Prize in Economics in 2009 for her work within the field \cite{ELINOR_OSTROM_NOBEL_LECTURE, 10.1257/aer.100.3.641}. We believe a monetary system and banking network should be a common resource because all users of it have an equal interest in the system; thus, the system should serve all interests equally by being governed as a common resource. Designing a governance model for a common requires clear rules for the boundaries, resources and actors in the system, which is described in this chapter. \cite{10.2139/ssrn.997834, ALLEN_CHRISTOPHER, ostrom2006}
\newline
Tagion has three main governance types that are listed in \cref{tab:governance_types} and elaborated in the next sub-sections. The common resources of Tagion are elaborated in \cref{sec:common_resources}.

\input{tab_governance_types}

\include{node_governance}
\include{economic_governance}
\include{system_upgrade_governance}
\include{common_resources}

